An automatic approach to find all possible calendar effects (periodic patterns) for an univariate time series

### 2021-02-23 paper/main.Rmd
adding application

```{r linear-scale}
library(scales)
library(tidyquant)
library(gghighlight)

@@

elec_zoom <- elec_linear + 
  coord_x_date(xlim = c("2018-02-01", "2018-02-28")) +
  gghighlight(date >as.Date("2018-02-05") & date < (as.Date("2018-02-12")),
              unhighlighted_params = list(colour = "grey")) + geom_line(aes(x = date_time, y = kwh, group = time))

@@

**Characterizing empirical distributions through quantiles**

@@

```{r raw-nqt}
elec_raw <- elec %>% 
  ggplot() +
  geom_density(aes(x = kwh)) +
  facet_wrap(~id, scales = "free_y") +
  xlab("demand (in kwh)")

elec_nqt <- elec %>% 
  dplyr::mutate(kwh_transformed = stats::qqnorm(kwh, plot.it = FALSE)$x) %>% 
  ggplot() +
  geom_density(aes(x = kwh_transformed))+
  facet_wrap(~id, scales = "free_y") +
  xlab("NQT demand (in kwh)")

@@

>>>>

```{r linear-scale, fig.cap = "Electricity demand for four households are shown in different facets from Jan-18 to Jun-18 in Fig a and it has been zoomed in for Feb-18 in Fig b, where a week in Feb-18 has been highlighted. From the scales of Fig a, it is apparent that they have different level of consumption but all of them have some periodic behavior in terms of regular peaks and troughs. It is not clear which all periodic patterns exist. In fig b, periodic pattern is zoomed in for a month and we can see weekly patterns for the entire period and daily pattern for the highlighted week."}
library(scales)
library(tidyquant)
library(gghighlight)

@@

elec_zoom <-  elec %>% 
  filter(date >as.Date("2018-02-01") & date < (as.Date("2018-02-28"))) %>% 
  ggplot(aes(x=date_time, y = kwh)) +
  facet_wrap(~id, scales = "free_y", ncol = 1, strip.position =  "right") +
  geom_smooth() +
  geom_point(alpha = 0.5, size = 0.1) +
  gghighlight(date >as.Date("2018-02-05") & date < (as.Date("2018-02-12")))

  # geom_rect(xmin = as.Date("2018-02-02"), xmax = as.Date("2018-02-04"), ymin = -Inf, ymax = Inf, fill = "pink", colour = pink)

# elec_zoom <- elec_linear + 
#   coord_x_date(xlim = c("2018-02-01", "2018-02-28")) +
#   gghighlight(date >as.Date("2018-02-05") & date < (as.Date("2018-02-12")),
#               unhighlighted_params = list(colour = "grey")) + geom_line(aes(x = date_time, y = kwh, group = time))

@@

**Characterizing empirical distributions through quantiles** ( write in the methodology maybe)

@@

```{r raw-nqt}
elec_raw <- elec %>% 
  ggplot() +
  geom_density(aes(x = kwh)) +
  facet_wrap(~id, scales = "free_y", ncol = 1) +
  xlab("demand (in kwh)")

elec_nqt <- elec %>% 
  dplyr::mutate(kwh_transformed = stats::qqnorm(kwh, plot.it = FALSE)$x) %>% 
  ggplot() +
  geom_density(aes(x = kwh_transformed))+
  facet_wrap(~id, scales = "free_y", ncol = 1) +
  xlab("NQT demand (in kwh)")

@@

```{r rank-household2and4}
elec <- read_rds(here("paper/data/elec.rds")) %>% 
  filter(date >= ymd("20180101"), date < ymd("20180701"))
rdbl <- c("Weekday" = "#d7191c", "Weekend" = "#2c7bb6")

all_harmony2 <- hakear::rank_harmonies(id2_tsibble,
   harmony_tbl = harmonies2,
   response = kwh,
   nperm = 200
 )

library(tictoc)
tic()
all_harmony4 <- hakear::rank_harmonies(id4_tsibble,
   harmony_tbl = harmonies4,
   response = kwh,
   nperm = 200
 )
toc()

```{r rank-harmonies}
all_harmony2 %>% kable()
all_harmony4 %>% kable()
```
